---
title: "Acoustic-Trawl Transect Generator"
author: "Kevin Stierhoff"
date: '`r format(Sys.time(), format = "%F %T", tz = "GMT", usetz = T)`'
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
# Install and Load packages
# Install and load pacman (library management package)
if (!require("pacman")) install.packages("pacman")

# Install and load required packages from CRAN ---------------------------------
pacman::p_load(tidyverse,swfscMisc,sf,mapview,here,
               rgdal,tcltk,knitr,leaflet,htmltools,
               pgirmess,bookdown,fs,beepr,rnaturalearth)

# Configure knitr chunk options
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      out.width = "100%")

# Create output directories
dir_create(here("Output/routes", 
                c("Compulsory","Adaptive","Nearshore","Saildrone")))

# Show map results
show.maps <- FALSE

# Randomize
do.random <- FALSE
save.csv  <- TRUE

# Mainland buffer distance for FSV and Saildrone transects
sd.buffer  <- 6 # nmi
fsv.buffer <- 80

# Transect spacing (nautical miles)
tx.spacing.fsv  <- 10.1 # For Lasker 
tx.spacing.sd   <- tx.spacing.fsv/2 # For Saildrone
tx.spacing.ns   <- tx.spacing.fsv/2 # For nearshore sampling

# Minimum transect length
min.tx.length <- 0 # nmi

# UCTD spacing (nautical miles)
uctd.spacing   <- 15

# Number of transects to remove from the start (if near Mexico)
rm.n.transects <- 0
```  

# Read baseline transect information
Information about the baseline transects, from which the final transects will be drawn, are stored in a .CSV file. The .CSV file contains the start location (`lat`, `long`), bearing (`brg_m` and `brg_t`), length (`distance_nmi`) of each baseline transect, and the length of the perpindicular transects (`tx_dist_nmi`). The `swfscMisc::destination()` function is used to compute the end of the transect. The resulting transects may be altered by changing the values of each of these parameters in the .CSV file.  

```{r read-info,message=FALSE}
# Read start locations
baseline.info <- read_csv(here("Data/Map/baselines.csv")) %>% 
  arrange(order)

# # Read summer survey waypoints
# waypoints <- read_csv(here("Data/waypoints.csv"))
# 
# # Convert waypoints to planned tranect lines
# tx_sf <- st_as_sf(waypoints, coords = c("long","lat"), crs = 4326) %>% 
#   group_by(type, line) %>% 
#   summarise(do_union = F) %>% 
#   st_cast("LINESTRING")

kable(baseline.info)
```  

# Create baseline transects
Baseline transects are created that are approximately parallel to the shoreline. Along the west coast of North America, between San Diego, CA and Vancouver Island, British Columbia, the coast is broken into three segments.  

```{r make-baselines,message=FALSE}
if (do.random) {
  # Create endpoints for segments used to generate random points
  locations <- baseline.info %>% 
    group_by(loc) %>% 
    mutate(
      lat1  = destination(lat, long, brg_t, 5, units = "nm", type = "ellipsoid")["lat"],
      long1 = destination(lat, long, brg_t, 5, units = "nm", type = "ellipsoid")["lon"]
    ) 
  
  # Create line segments 
  random.segments <- select(locations, loc, lat, long) %>% 
    bind_rows(select(locations, loc, lat = lat1, long = long1)) %>% 
    st_as_sf(coords = c("long", "lat"), crs = 4326) %>% 
    group_by(loc) %>% 
    summarise(do_union = F) %>% 
    st_cast("LINESTRING")
  
  # Segmentize and select random points
  random.points <- random.segments %>% 
    st_segmentize(200) %>%    # Distance between points; 200 m ~ 0.1 nmi
    st_cast("MULTIPOINT") %>% # Cast as points
    st_cast("POINT") %>% 
    mutate(
      long = as.data.frame(st_coordinates(.))$X,
      lat = as.data.frame(st_coordinates(.))$Y) %>% 
    group_by(loc) %>% 
    sample_n(1) %>% 
    left_join(select(baseline.info, -long, -lat)) %>% 
    mutate(
      lat1  = destination(lat, long, brg_t, dist_nmi, units = "nm", type = "ellipsoid")["lat"],
      long1 = destination(lat, long, brg_t, dist_nmi, units = "nm", type = "ellipsoid")["lon"]
    ) %>% 
    st_set_geometry(NULL)
  
  # Create baselines from randomized start locations
  baselines <- select(random.points, loc, lat, long) %>% 
    rbind(select(random.points, loc, lat = lat1, long = long1)) %>% 
    st_as_sf(coords = c("long", "lat"), crs = 4326) %>%
    group_by(loc) %>% 
    summarise(do_union = F) %>% 
    st_cast("LINESTRING")
  
  save(locations, random.segments, random.points, baselines,
       file = here("Data/Map/randomized_baseline_data.Rdata"))
} else {
  # Load randomized points
  load(file = here("Data/Map/randomized_baseline_data.Rdata"))
}
```

# Segmentize baseline transects for FSV sampling
The start points of the transects that will be drawn perpendicular to the coast are generated by segmentizing the baseline transects at 10 nmi intervals.

```{r segmentize-baselines,message=FALSE}
# Create segments from baselines
# dfMaxLength is 10 nautical miles (or 18520 m)
segments <- st_segmentize(baselines, dfMaxLength = 1852 * tx.spacing.fsv)

# Extract points from segments and determine the offshore endpoints
points <- st_cast(segments, "POINT") %>% 
  left_join(select(locations, order, loc, brg_t, tx_dist_nmi, brg_tx)) %>% 
  mutate(long = as.data.frame(st_coordinates(.))$X,
         lat = as.data.frame(st_coordinates(.))$Y) %>% 
  arrange(order, lat) %>% 
  mutate(id  = seq(n())) %>% 
  st_set_geometry(NULL) %>% 
  group_by(id) %>% 
  mutate(
    lat1  = destination(lat, long, brg_tx, tx_dist_nmi, units = "nm")["lat"],
    long1 = destination(lat, long, brg_tx, tx_dist_nmi, units = "nm")["lon"]
  )

# Create transect lines from points
transects <- select(points, id, loc, lat, long) %>% 
  bind_rows(select(points, id, loc, lat = lat1, long = long1)) %>% 
  st_as_sf(coords = c("long", "lat"), crs = 4326) %>% 
  group_by(loc, id) %>% 
  summarise(do_union = F) %>% 
  st_cast("LINESTRING") %>% 
  filter(id > rm.n.transects) %>% 
  mutate(id = id - rm.n.transects)

if (show.maps) {
  mapview(baselines) + mapview(transects, zcol = "loc")  
}

```

# Segmentize baseline transects for Saildrone sampling
The start points of the transects that will be drawn perpendicular to the coast are generated by segmentizing the baseline transects at `r tx.spacing.sd` nmi intervals.

```{r segmentize-baselines-sd,message=FALSE}
# Create segments from baselines
# dfMaxLength is 10 nautical miles (or 18520 m)
segments.sd <- st_segmentize(baselines, dfMaxLength = 1852 * tx.spacing.sd)

# Extract points from segments and determine the offshore endpoints
points.sd <- st_cast(segments.sd, "POINT") %>% 
  left_join(select(locations, order, loc, brg_t, tx_dist_nmi, brg_tx)) %>% 
  mutate(long = as.data.frame(st_coordinates(.))$X,
         lat = as.data.frame(st_coordinates(.))$Y) %>% 
  arrange(order, lat) %>% 
  mutate(id  = seq(n())) %>% 
  st_set_geometry(NULL) %>% 
  group_by(id) %>% 
  mutate(
    lat1  = destination(lat, long, brg_tx, tx_dist_nmi, units = "nm")["lat"],
    long1 = destination(lat, long, brg_tx, tx_dist_nmi, units = "nm")["lon"]
  )

# Create transect lines from points
transects.sd <- select(points.sd, id, loc, lat, long) %>% 
  bind_rows(select(points.sd, id, loc, lat = lat1, long = long1)) %>% 
  st_as_sf(coords = c("long", "lat"), crs = 4326) %>% 
  group_by(loc, id) %>% 
  summarise(do_union = F) %>% 
  st_cast("LINESTRING") %>% 
  filter(id > rm.n.transects*2) %>% 
  mutate(id = id - rm.n.transects*2)

if (show.maps) {
  mapview(baselines) + mapview(transects.sd, zcol = "loc")
}
```

# Segmentize baseline transects for nearshore sampling
The start points of the transects that will be drawn perpendicular to the coast are generated by segmentizing the baseline transects at `r tx.spacing.ns` nmi intervals.

```{r segmentize-baselines-ns,message=FALSE}
# Create segments from baselines
# dfMaxLength is 10 nautical miles (or 18520 m)
segments.ns <- st_segmentize(baselines, dfMaxLength = 1852 * tx.spacing.ns)

# Extract points from segments and determine the offshore endpoints
points.ns <- st_cast(segments.ns, "POINT") %>% 
  left_join(select(locations, order, loc, brg_t, tx_dist_nmi, brg_tx)) %>% 
  mutate(long = as.data.frame(st_coordinates(.))$X,
         lat = as.data.frame(st_coordinates(.))$Y) %>% 
  arrange(order, lat) %>% 
  mutate(id  = seq(n())) %>% 
  st_set_geometry(NULL) %>% 
  group_by(id) %>% 
  mutate(
    lat1  = destination(lat, long, brg_tx, tx_dist_nmi, units = "nm")["lat"],
    long1 = destination(lat, long, brg_tx, tx_dist_nmi, units = "nm")["lon"]
  )

# Create transect lines from points
transects.ns <- select(points.ns, id, loc, lat, long) %>% 
  bind_rows(select(points.ns, id, loc, lat = lat1, long = long1)) %>% 
  # bind_rows(points.ns.ci) %>% 
  st_as_sf(coords = c("long", "lat"), crs = 4326) %>% 
  group_by(loc, id) %>% 
  summarise(do_union = F) %>% 
  st_cast("LINESTRING") %>% 
  filter(id > rm.n.transects*2) %>% 
  mutate(id = id - rm.n.transects*2)

if (show.maps) {
  mapview(baselines) + mapview(transects.ns, zcol = "loc")
}
```

# Load other GIS layers

```{r load-gis-data, results = FALSE}
# Read bathy contours shapefile 
bathy_contours <- st_read(here("Data/GIS/bathy_contours.shp")) %>% 
  st_transform(4326) %>% 
  rename(Depth = Contour)

# Read 5m isobath polygon
bathy_5m <- st_read(here("Data/GIS/bathy_5m_polygon.shp"))

# Read waypoint polygon
wpt.polygon <- st_read(here("Data/GIS/waypoint_polygon.shp")) 

# Read Vancouver Island MPA polygon
si.mpa <- read_csv(here("Data/GIS/scott_islands_mpa_boundary.csv")) %>% 
  st_as_sf(coords = c("long", "lat"), crs = 4326) %>% 
  summarise(do_union = F) %>% 
  st_cast("POLYGON")

# Export to shapefile
st_write(si.mpa, here("Data/GIS/scott_islands_mpa_polygon.shp"), 
         delete_layer = TRUE)

# Read EEZ files
eez.us <- st_read(here("Data/GIS/eez_us.shp"))
eez.mx <- st_read(here("Data/GIS/eez_mex.shp"))
eez.ca <- st_read(here("Data/GIS/eez_canada.shp"))

# Download worldwide states 
# and filter for Western N. Am.
states <- ne_states(
  country = c("Canada",
              "United States of America",
              "Mexico"),
  returnclass = 'sf') %>% 
  filter(name %in% c("California","Oregon",
                     "Washington","Nevada",
                     "British Columbia",
                     "Baja California",
                     "Baja California Sur")) %>% 
  st_cast("POLYGON") %>% 
  mutate(area = st_area(.)) %>% 
  arrange(desc(area)) 

# Buffer mainland to clip Saildrone and Lasker transects
states.buff.sd <- rbind(
  filter(states, name %in% c("Oregon","Washington","Nevada",
                     "British Columbia","Baja California",
                     "Baja California Sur")),
  filter(states, name == "California", as.numeric(area) > 258366741)) %>% 
  summarise() %>% 
  st_buffer(sd.buffer/60)

states.buff.fsv <- states %>% 
  filter(name == "California",
         as.numeric(area) > 258366741) %>% 
  summarise() %>% 
  st_buffer(fsv.buffer/60)
```

# Draw final transects
Transects are then clipped using the 5-m and 1000-fm isobaths to create transects that span the contintental shelf, or where the shelf is narrow, transects that are approximately 35-nmi long.

```{r draw-transects, message=FALSE, results='hide', warning=FALSE}
# Import the 5m bathy polygon used to clip the transects on the eastern edge
inshore.clip <- st_read(here("Data/GIS/bathy_5m_polygon.shp")) %>% 
  lwgeom::st_make_valid()

# Read offshore clip polygon
offshore.clip <- st_read(here("Data/GIS/waypoint_polygon.shp"))

# Create a clipping polygon around central transects
central.clip <- transects %>% 
  filter(loc == "central") %>% 
  st_cast("POINT") %>% 
  st_union() %>% 
  st_convex_hull() %>% 
  st_sf() %>% 
  st_buffer(5/60)

# Remove transects.final if it exists
if (exists("transects.final")) rm(transects.final)

# Clip each set of FSV transects using the inshore and offshore polygons
for (i in unique(transects$loc)) {
  tx.temp <- ungroup(filter(transects, loc == i)) %>% 
    st_difference(inshore.clip) %>% 
    st_intersection(offshore.clip) %>% 
    select(loc, id)
  
  # If the northern transects, also clip using the polygon
  # around the central transects
  if (i == "north") {
    tx.temp <- st_difference(tx.temp, central.clip) %>% 
      st_difference(si.mpa) %>% 
      select(loc, id)
  }
  
  if (i == "south") {
    tx.temp <- st_intersection(tx.temp, states.buff.fsv) %>% 
    select(loc, id)
  }
  
  # Combine results
  if (exists("transects.final")) {
    transects.final <- rbind(transects.final, tx.temp)
  } else {
    transects.final <- tx.temp
  }
}

# Remove transects.final.sd if it exists
if (exists("transects.final.sd")) rm(transects.final.sd)

# Clip each set of FSV transects using the inshore and offshore polygons
for (i in unique(transects.sd$loc)) {
  tx.temp <- ungroup(filter(transects.sd, loc == i)) %>% 
    st_difference(inshore.clip) %>% 
    st_intersection(offshore.clip) %>% 
    st_intersection(states.buff.sd) %>% 
    select(loc, id)
  
  # If the northern transects, also clip using the polygon
  # around the central transects
  if (i == "north") {
    tx.temp <- st_difference(tx.temp, central.clip) %>% 
      st_intersection(offshore.clip) %>% 
      select(loc, id)
  }
  
  # Combine results
  if (exists("transects.final.sd")) {
    transects.final.sd <- rbind(transects.final.sd, tx.temp)
  } else {
    transects.final.sd <- tx.temp
  }
}

# Remove transects.final.sd if it exists
if (exists("transects.final.ns")) rm(transects.final.ns)

# Clip each set of FSV transects using the inshore and offshore polygons
for (i in unique(transects.ns$loc)) {
  tx.temp <- ungroup(filter(transects.ns, loc == i)) %>% 
    st_difference(inshore.clip) %>% 
    st_intersection(offshore.clip) %>% 
    st_intersection(states.buff.sd) %>% 
    select(loc, id)
  
  # If the northern transects, also clip using the polygon
  # around the central transects
  if (i == "north") {
    tx.temp <- st_difference(tx.temp, central.clip) %>%
      st_intersection(offshore.clip) %>% 
      select(loc, id)
  }
  
  # Combine results
  if (exists("transects.final.ns")) {
    transects.final.ns <- rbind(transects.final.ns, tx.temp)
  } else {
    transects.final.ns <- tx.temp
  }
}

# Calculate transect distances
transects.final <- transects.final %>% 
  mutate(distance = as.numeric(st_length(.))/1852) %>% # Distance; nmi
  filter(distance > 8) %>% 
  mutate(id = rank(id)) %>% 
  rename(transect = id) %>% 
  arrange(transect)

transects.final.sd <- transects.final.sd %>% 
  st_cast("LINESTRING") %>% 
  mutate(distance = as.numeric(st_length(.))/1852, # Distance; nmi
         type = "Saildrone") %>% # Define type as Saildrone 
  rename(transect = id) %>% 
  arrange(transect) %>% 
  filter(distance > min.tx.length)

# Read Channel Island nearshore transect waypoints
transects.ns.ci <- read_csv(here("Data/Nav/waypoints_channel_islands.csv")) %>% 
  st_as_sf(coords = c("long", "lat"), crs = 4326) %>%
  select(loc = region, id) %>% 
  mutate(id = id + max(points.ns$id)) %>% 
  group_by(loc, id) %>% 
  summarise(do_union = F) %>% 
  st_cast("LINESTRING")

transects.final.ns <- transects.final.ns %>% 
  st_cast("LINESTRING") %>% 
  rbind(transects.ns.ci) %>% 
  mutate(distance = as.numeric(st_length(.))/1852, # Distance; nmi
         type = "Nearshore") %>% # Define type as Saildrone 
  rename(transect = id) %>% 
  arrange(transect) %>% 
  filter(distance > min.tx.length)

# Convert transects to waypoints
waypoints.final <- transects.final %>% 
  st_cast("MULTIPOINT") %>% 
  st_cast("POINT") %>% 
  mutate(id  = seq(n()))

waypoints.final.sd <- transects.final.sd %>% 
  st_cast("MULTIPOINT") %>% 
  st_cast("POINT") %>% 
  mutate(id  = seq(n()))

waypoints.final.ns <- transects.final.ns %>% 
  st_cast("MULTIPOINT") %>% 
  st_cast("POINT") %>% 
  mutate(id  = seq(n()))

# Convert waypoints to df for writeGPX
waypoints.final.df <- waypoints.final %>% 
  mutate(
    long = as.data.frame(st_coordinates(.))$X,
    lat  = as.data.frame(st_coordinates(.))$Y) %>% 
  st_set_geometry(NULL) %>% 
  select(transect, id, long, lat) %>% 
  as.data.frame()

waypoints.final.sd.df <- waypoints.final.sd %>% 
  mutate(
    long = as.data.frame(st_coordinates(.))$X,
    lat  = as.data.frame(st_coordinates(.))$Y) %>% 
  st_set_geometry(NULL) %>% 
  select(transect, id, long, lat, type) %>% 
  as.data.frame()

waypoints.final.ns.df <- waypoints.final.ns %>% 
  mutate(
    long = as.data.frame(st_coordinates(.))$X,
    lat  = as.data.frame(st_coordinates(.))$Y) %>% 
  st_set_geometry(NULL) %>% 
  select(transect, id, long, lat, type) %>% 
  as.data.frame()

waypoint.type <- waypoints.final.df %>% 
  group_by(transect) %>% 
  slice(1) %>% 
  # Make odd numbered transects Compulsory; others Adaptive
  mutate(type = case_when(
    transect %% 2 == 0 ~ "Adaptive",
    TRUE ~ "Compulsory")) %>% 
  # Create 10 nmi-wide compulsory spacing between Cape Flattery and Newport, OR
  # and S of Pt. Conception
  mutate(type = case_when(
    between(lat, 44.6, 48.55) ~ "Compulsory",
    lat < 34.5 ~ "Compulsory",
    TRUE ~ type)) %>% 
  ungroup()

# Add transect types to FSV transects and waypoints
transects.final <- transects.final %>% 
  left_join(select(waypoint.type, transect, type))

# mapview(transects.final, zcol = "type")

waypoints.final <- waypoints.final %>% 
  left_join(select(waypoint.type, transect, type)) 

waypoints.final.df <- waypoints.final.df %>% 
  left_join(select(waypoint.type, transect, type)) 

# ggplot(waypoints.final.df,
#        aes(long, lat, colour = type, group = transect)) +
#   geom_point() +
#   geom_path() +
#   coord_map()

# Get map boundaries
bounds.long <- range(waypoints.final.df$long)
bounds.lat  <- range(waypoints.final.df$lat)
```  

# Create UCTD stations

Along each transect, UCTD transects are placed at `r uctd.spacing` nmi intervals.

```{r uctd-stations}
# Buffer transect waypoints to remove end stations
uctd.wpt.buff <- waypoints.final %>% 
  st_buffer(5/60)

# dfMaxLength is 10 nautical miles (or 18520 m)
uctd.segments <- st_segmentize(transects.final, dfMaxLength = 1852*uctd.spacing)

# Extract points from segments and determine the offshore endpoints
uctd.final <- uctd.segments %>% 
  st_cast("MULTIPOINT") %>%
  st_cast("POINT") %>%
  # st_difference(uctd.wpt.buff) %>% 
  mutate(id  = seq(n())) 

# Convert waypoints to df for writeGPX
uctd.final.df <- uctd.final %>% 
  mutate(
    long = as.data.frame(st_coordinates(.))$X,
    lat  = as.data.frame(st_coordinates(.))$Y) %>% 
  st_set_geometry(NULL) %>% 
  select(transect, id, long, lat) %>% 
  as.data.frame()
```

# View final transects

```{r view-results, echo=F, out.height='10in', out.width='100%'}
# Leaflet tile options; set both to T if caching
useCachedTile  <- F # Use cached tiles
useCrossOrigin <- F # USe cross origin

# Create color pallette for planned transects
txPal    <- colorFactor(c("red","blue","green","orange","magenta"), 
                        c("Adaptive","Compulsory","Mammal","Nearshore","Saildrone"))

leaflet() %>% 
  # Add provider tiles; # http://leaflet-extras.github.io/leaflet-providers/preview/index.html
  addProviderTiles(providers$Esri.OceanBasemap, 
                   options = tileOptions(useCache = useCachedTile,
                                         crossOrigin = useCrossOrigin)) %>% 
  # Add bathymetry contours
  addPolylines(data = bathy_contours, color = "white", weight = 2, 
               label = ~paste(Depth, "m"), group = "Bathymetry Contours") %>% 
   # Add EEZ files
  addPolygons(data = eez.us, color = "#000414", weight = 2, 
              fillColor = "transparent",
              label = ~htmlEscape("U.S. Exclusive Economic Zone"), group = "EEZs") %>%
  addPolygons(data = eez.mx, color = "#000414", weight = 2, 
              fillColor = "transparent",
              label = ~htmlEscape("Mexico Exclusive Economic Zone"), group = "EEZs") %>%
  addPolygons(data = eez.ca, color = "#000414", weight = 2, 
              fillColor = "transparent",
              label = ~htmlEscape("Canada Exclusive Economic Zone"), group = "EEZs") %>%
  # Add transect lines and waypoints
  addPolylines(data = transects.final, color = ~txPal(type), weight = 3, 
               label = ~paste("Transect: ", transect, 
                              " , Distance: ", round(distance, 1), " nmi",
                              sep = ""), popup = ~htmlEscape(transect), 
               group = "Planned Transects-FSV") %>% 
  addCircleMarkers(data = waypoints.final,
                   radius = 3, color = ~txPal(type), stroke = TRUE,
                   opacity = 0.8, fillOpacity = 1, weight = 1, 
                   label = ~paste("Transect:", transect),
                   group = "Planned Transects-FSV") %>%
  addPolylines(data = transects.final.ns, color = ~txPal(type), weight = 3, 
               label = ~paste("Nearshore Transect: ", transect, 
                              " , Distance: ", round(distance, 1), " nmi",
                              sep = ""), popup = ~htmlEscape(transect), 
               group = "Planned Transects-Nearshore") %>%
  addCircleMarkers(data = waypoints.final.ns,
                   radius = 3, color = ~txPal(type), stroke = TRUE,
                   opacity = 0.8, fillOpacity = 1, weight = 1, 
                   label = ~paste("Transect:", transect),
                   group = "Planned Transects-Nearshore") %>%
  addPolylines(data = transects.final.sd, color = ~txPal(type), weight = 3,
               label = ~paste("Saildrone Transect: ", transect,
                              " , Distance: ", round(distance, 1), " nmi",
                              sep = ""), popup = ~htmlEscape(transect),
               group = "Planned Transects-Saildrone") %>%
  addCircleMarkers(data = waypoints.final.sd,
                   radius = 3, color = ~txPal(type), stroke = TRUE,
                   opacity = 0.8, fillOpacity = 1, weight = 1,
                   label = ~paste("Transect:", transect),
                   group = "Planned Transects-Saildrone") %>%
  addCircleMarkers(data = uctd.final,
                   radius = 3, color = "#000000", stroke = TRUE, 
                   weight = 1,
                   opacity = 0.8, fillOpacity = 1, fillColor =  "white", 
                   label = ~paste("Transect:", id),
                   group = "UCTD Stations") %>%
  # Add clipping polygons
  addPolygons(data = wpt.polygon, color = "#000414", weight = 2, 
              fillColor = "transparent",
              label = ~htmlEscape("Offshore Mask"), group = "Offshore Mask") %>%
  addPolygons(data = bathy_5m, color = "#000414", weight = 2, 
              fillColor = "transparent",
              label = ~htmlEscape("Inshore Mask"), group = "Inshore Mask") %>%
  addPolygons(data = central.clip, color = "#000414", weight = 2, 
              fillColor = "transparent",
              label = ~htmlEscape("Central Mask"), group = "Central Mask") %>%
  addPolygons(data = states.buff.fsv, color = "#000414", weight = 2,
              fillColor = "transparent",
              label = ~htmlEscape("FSV Mask"), group = "FSV Mask") %>%
  # Add minimap
  addMiniMap(position = "topright") %>% 
  # Add scale bar
  addScaleBar(position = "bottomright") %>%
  # Add map coordinates
  addMouseCoordinates() %>% 
  # Add measurement tool
  addMeasure(primaryLengthUnit = "miles", secondaryLengthUnit = "km",
             primaryAreaUnit = "sqmiles", secondaryAreaUnit = "sqmeters",
             position = "topleft") %>% 
  # Add layer controls
  addLayersControl(
    overlayGroups = c("Planned Transects-FSV",
                      "Planned Transects-Nearshore",
                      "Planned Transects-Saildrone",
                      "Bathymetry Contours", "UCTD Stations",
                      "Inshore Mask", "Offshore Mask", 
                      "Central Mask", "FSV Mask", "EEZs"),
    options = layersControlOptions(collapsed = F)) %>% 
  hideGroup(c("Inshore Mask", "Offshore Mask", "UCTD Stations",
              "Planned Transects-Saildrone",
              "Central Mask", "FSV Mask")) %>%  
  fitBounds(min(bounds.long), min(bounds.lat),
            max(bounds.long), max(bounds.lat))
```


# Export lines to Rose Point-compatible .csv route files
Once created, transect lines are exported to .csv format for import to Rose Point, where they may be edited further.

```{r export-csv}
# Creat an order vector
order.vec <- rep(c(1,2,2,1), nrow(waypoints.final.df))[1:nrow(waypoints.final.df)]

# Write waypoints to CSV file for Rose Point import
waypoints.final.csv <- waypoints.final.df %>% 
  mutate(loc = rep(c(1,2), n()/2),
         order = order.vec,
         transect = sprintf("%03d", transect),
         # id    = paste(transect, loc, sep = "."),
         id = case_when(
           type == "Compulsory" ~ paste(transect, ".", loc, "C", sep = ""),
           type == "Adaptive"   ~ paste(transect, ".", loc, "A", sep = "")
         )) %>% 
  arrange(transect, order)

# Write waypoints to CSV file for Rose Point import
waypoints.final.sd.csv <- waypoints.final.sd.df %>% 
  mutate(loc = rep(c(1,2), n()/2),
         # order = order.vec,
         transect = sprintf("%03d", transect),
         id    = paste(transect, ".", loc, "S", sep = "")) 

# Write waypoints to CSV file for Rose Point import
waypoints.final.ns.csv <- waypoints.final.ns.df %>% 
  mutate(loc = rep(c(1,2), n()/2),
         # order = order.vec,
         transect = sprintf("%03d", transect),
         id    = paste(transect, ".", loc, "N", sep = "")) 

# Create output directory
dir_create(here("Output", c("waypoints")))

# Write all waypoints to one CSV (to import one route)
write_csv(select(waypoints.final.csv, id, lat, long), 
          here("Output/waypoints/transect_wpts.csv"))

write_csv(select(waypoints.final.sd.csv, id, lat, long), 
          here("Output/waypoints/transect_wpts_sd.csv"))

write_csv(select(waypoints.final.ns.csv, id, lat, long), 
          here("Output/waypoints/transect_wpts_ns.csv"))

if (save.csv) {
  # Create output directories
  dir_create(here("Output/routes", c("Compulsory", "Adaptive", "Saildrone", "Nearshore")))
  
  # Write waypoints from individual files to multiple CSV to create single routes
  for (i in unique(waypoints.final.csv$transect)) {
    wpts.sub <- waypoints.final.csv %>% 
      filter(transect == i, type == "Compulsory") %>% 
      select(id, lat, long) 
    
    write_csv(wpts.sub, here("Output/routes/Compulsory", paste(i, "C.csv", sep = "")))
  }
  
  for (i in unique(waypoints.final.csv$transect)) {
    wpts.sub <- waypoints.final.csv %>% 
      filter(transect == i, type == "Adaptive") %>% 
      select(id, lat, long) 
    
    write_csv(wpts.sub, here("Output/routes/Adaptive", paste(i, "A.csv", sep = "")))
  }
  
  # Write waypoints from individual files to multiple CSV to create single routes
  for (i in unique(waypoints.final.sd.csv$transect)) {
    wpts.sub <- waypoints.final.sd.csv %>% 
      filter(transect == i) %>% 
      select(id, lat, long) 
    
    write_csv(wpts.sub, here("Output/routes/Saildrone", paste(i, "S.csv", sep = "")))
  }
  
  # Write waypoints from individual files to multiple CSV to create single routes
  for (i in unique(waypoints.final.ns.csv$transect)) {
    wpts.sub <- waypoints.final.ns.csv %>% 
      filter(transect == i) %>% 
      select(id, lat, long) 
    
    write_csv(wpts.sub, here("Output/routes/Nearshore", paste(i, "N.csv", sep = "")))
  }
  
  # Write waypoints to CSV file
  uctd.final.csv <- uctd.final.df %>% 
    mutate(order = seq_along(id),
           id    = paste("UCTD", order)) %>% 
    select(id, lat, long)
  
  write_csv(uctd.final.csv, here("Output/waypoints/uctd_wpts.csv"))  
}

if (do.random) {
  # # Write transects to GPX file
  # writeOGR(as(transects.final, "Spatial"),
  #          dsn             = here("Output/transect_lines.gpx"),
  #          driver          = "GPX",
  #          layer           = "track_points",
  #          dataset_options = "GPX_USE_EXTENSIONS=YES",
  #          overwrite_layer = T)
  # 
  # # Write waypoints to GPX file 
  # writeGPX(waypoints.final.df, 
  #          filename = here("Output/transect_wpts.gpx"), 
  #          type = "w")
  
    # # Write baselines to GPX file
  # writeOGR(as(baselines, "Spatial"),
  #          dsn             = here("Output/baselines.gpx"),
  #          driver          = "GPX",
  #          layer           = "track_points",
  #          dataset_options = "GPX_USE_EXTENSIONS=YES",
  #          overwrite_layer = T) 
  
  # # Write UCTD stations to GPX file 
  # writeGPX(uctd.final.df, 
  #          filename = here("Output/uctd_wpts.gpx"), 
  #          type = "w")
}
```

Fin!

```{r}
beep(4)
```

