---
output:
  bookdown::html_document2:
    toc: no
    toc_float: no
    number_sections: no
css: css/ast.css
---

```{r setup,echo=F,message=F,warning=F,error=F,include=F}
# Install and load pacman (library management package)
if (!require("pacman")) install.packages("pacman")

# Install and load required packages from CRAN ---------------------------------
pacman::p_load(tidyverse,raster,cowplot,DBI,odbc,RSQLite,scatterpie,ggspatial,vroom,
               reshape2,readxl,lubridate,rnaturalearth,sf,rgeos,here,naniar,mapview,
               shadowtext,knitr,ggrepel,fs,plotly,leaflet,leaflet.extras,bookdown,
               leaflet.minicharts,maptools,htmltools,leafem,DT,rworldmap,rworldxtra,
               lwgeom,rayshader)

# Install and load required packages from Github -------------------------------
# surveyR
pacman::p_load_gh("kstierhoff/surveyR")
# atm
pacman::p_load_gh("kstierhoff/atm")
# rnaturalearth data
pacman::p_load_gh("ropenscilabs/rnaturalearthdata")
pacman::p_load_gh("ropenscilabs/rnaturalearthhires")

# determines method of table generation (whether kable or xtable) for best formatting
doc.type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
doc.name <- knitr::current_input()
if (is.null(doc.type)) {doc.type <- "html"}
if (is.null(doc.name)) {doc.name <- "plotCUFES.Rmd"}

# global knitr chunk options
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, out.width = '100%',
  fig.align = "center", dev = "png", dev.args = list(type = "cairo"), dpi = 150
)
```

```{r user-input,include=FALSE}
# Get project name from directory name
prj.name <- last(unlist(str_split(here(), "/")))

# Get all settings files
settings.files <- dir(here("Doc/settings"))

# Source survey settings file
prj.settings <- settings.files[str_detect(settings.files, paste0("settings_", prj.name, ".R"))]
source(here("Doc/settings", prj.settings))
```

```{r processing-controls}
# Control script behavior (usually T)
save.figs       <- F # Resave figures
get.nav         <- F # Download nav data from ERDDAP
copy.files      <- T # Copy data files from data to plotBio directory
overwrite.files <- T # Overwrite existing files when copying (not CSV, see below)
resize.map      <- F # Scale map to fit survey data
```

```{r copy-files, include=F}
if (copy.files) {
  # Create data directories
  dir_create(here("Data/CUFES"))
  
  # Copy CUFES files
  cufes.file <- dir_ls(file.path(survey.dir[survey.vessel.primary], "DATA/BIOLOGICAL/CUFES"), 
                       regex = cufes.db.sqlite)
  file_copy(cufes.file, here("Data/CUFES"), overwrite = overwrite.files)
}
```

```{r process-nav}
if (get.nav) {
  # Load existing nav data
  if (file.exists(here("Data/Nav/nav_data.Rdata"))) {
    load(here("Data/Nav/nav_data.Rdata"))
    
    # Calculate difference between max nav time and now
    nav.lag <- difftime(now(tzone = "UTC"), max(ymd_hms(nav$time)), units = "hours")
    
    # Get new erddap start date from max date
    erddap.survey.start <- max(date(nav$time))
  }
  
  if (nav.lag >= 24) {
    # Generate ERDDAP URL
    dataURL <- URLencode(paste(
      "http://coastwatch.pfeg.noaa.gov/erddap/tabledap/fsuNoaaShip",
      erddap.vessel, ".csv0?", erddap.vars,
      "&time>=", erddap.survey.start, "&time<=", erddap.survey.end,
      sep = ""))
    
    # Download and parse ERDDAP nav data
    nav.temp <- read_csv(dataURL, lazy = FALSE,
                         col_names = erddap.headers) %>% 
      mutate(long     = long - 360,
             SOG      = SOG * 1.94384,
             SST      = na_if(SST, NaN),
             wind_brg = case_when(
               wind_dir < 180 ~ wind_dir + 180,
               TRUE ~ wind_dir - 180),
             wind_angle = (wind_dir/360)*2*pi,
             leg      = paste("Leg", 
                              cut(as.numeric(date(time)), 
                                  leg.breaks, 
                                  labels = FALSE))) %>%
      filter(is.nan(SOG) == FALSE, SOG > 0, SOG < 15,
             between(lat, min(survey.lat), max(survey.lat)), 
             between(long, min(survey.long), max(survey.long)))
    
    # Append new nav data
    if (exists("nav")) {
      nav <- bind_rows(nav, nav.temp) %>% 
        distinct()
    } else {
      nav <- nav.temp
    }
  }
  
  # Convert nav to spatial
  nav.sf <- st_as_sf(nav, coords = c("long","lat"), crs = crs.geog) 
  
  # Cast nav to transects
  nav.paths.sf <- nav.sf %>% 
    group_by(leg) %>% 
    summarise(do_union = F) %>% 
    st_cast("LINESTRING")
  
  # Save results
  save(nav, nav.sf, nav.paths.sf, file = here("Data/Nav/nav_data.Rdata"))
} else {
  # Load nav data
  load(here("Data/NAV/nav_data.Rdata"))
}

# Read transect waypoints
wpts <- read_csv(here("Data/Nav", wpt.filename))

# Convert planned transects to sf; CRS = crs.geog
wpts.sf <- wpts %>% 
  filter(Type %in% wpt.types) %>% 
  st_as_sf(coords = c("Longitude","Latitude"), crs = crs.geog)

transects.sf <- wpts.sf %>% 
  group_by(Type, Transect, Region) %>% 
  summarise(do_union = F) %>% 
  st_cast("LINESTRING")

# Create gps.csv file from nav to replace missing data in Echoview
nav.gps <- nav %>% 
  mutate(GPS_date = format(time, format = "%F"),
         GPS_time = format(time, format = "%T")) %>% 
  select(GPS_date, GPS_time, latitude = lat, longitude = long)

write_csv(nav.gps, here("Output/nav.gps.csv"))

# Get most recent vessel position for plotting
nav.now <- tail(nav.sf, 1) %>% 
  mutate(label = paste("Last position:", time, "UTC"))
```

```{r process-cufes}
# Read CUFES data
cufes.filename <- list.files(here("Data/CUFES"), pattern = "*.sqlite")
cufes.con      <- dbConnect(SQLite(), dbname = here("Data/CUFES", cufes.db.sqlite))
cufes.raw <- tbl(cufes.con, "cufessqlite") %>%
  collect() %>% 
  mutate(
    Start = case_when(
      cufes.date.format == "mdy" ~ mdy_hms(Start), #"06/01/2019-15:43:00"
      cufes.date.format == "ymd" ~ ymd_hms(Start)),#"1996-03-15 15:43:00 -08:00"
    Stop = case_when(
      cufes.date.format == "mdy" ~ mdy_hms(Stop), #"06/01/2019-15:43:00"
      cufes.date.format == "ymd" ~ ymd_hms(Stop)),#"1996-03-15 15:43:00 -08:00"
    Duration = as.numeric(difftime(Stop, Start, units = "mins")),
    Year = year(Start),
    AllEggs = SardineEggs + AnchovyEggs + JackMackerelEggs) %>% 
  rename(lat = StartLatitude, long = StartLongitude) %>% 
  filter(!is.na(lat), !is.na(long), !is.na(Stop)) %>% 
  project_df(to = crs.proj)

# Close connection
dbDisconnect(cufes.con)

# save raw cufes table to CSV
write.csv(cufes.raw, file = here("Output/cufes_raw.csv"), 
          quote = F, row.names = F)

# Process CUFES data
cufes <- cufes.raw %>% 
  # Convert cufes to long format for plotting
  select(
    SampleNumber, Year, Ship, Cruise, lat, long, X, Y, Duration, 
    SardineEggs, AnchovyEggs, JackMackerelEggs, SquidEggs, HakeEggs, OtherFishEggs,
    Comments) %>%
  gather(Species, Counts, -SampleNumber, -Year, -Ship, -Cruise, 
         -lat, -long, -X, -Y, -Duration, -Comments) %>% 
  mutate(Density = Counts/Duration/0.64,
         # Create bins for defining point size in NASC plots
         bin = cut(Density, cufes.breaks, include.lowest = T),
         bin.level = as.numeric(bin)) %>% 
  left_join(select(cufes.raw, SampleNumber, Start, Stop)) 

# Save processed cufes to CSV
write.csv(cufes, file = here("Output/cufes_proc.csv"), 
          quote = F, row.names = F)

# Prepare CUFES data for plotting ----------------------------------------------
# Select CUFES sample with zero density for plotting
cufes.neg <- filter(cufes.raw, AllEggs == 0) %>% 
  mutate(bin.level = 1) %>% 
  select(X, Y, SampleNumber)

# Identify bad CUFES samples
cufes.bad <- filter(cufes.raw, Duration <= 0)

save(cufes.bad, file = here("Output/cufes_bad.Rdata"))

# Remove bad samples from CUFES
cufes <- cufes %>% 
  filter(!SampleNumber %in% cufes.bad$SampleNumber)

# Write CUFES data from current survey to CSV
write.csv(cufes, file = here("Output/cufes_data.csv"), quote = F)

# Create bins for defining point size in NASC plots
cufes <- cufes %>% 
  mutate(bin = cut(Density, cufes.breaks, include.lowest = T),
         bin.level = as.numeric(bin))

# Project CUFES data from CPS
cufes.plot <- cufes %>% 
  filter(Density > 0, Species %in% cufes.plot.spp) %>%
  arrange(desc(Density))

# Project CUFES data from squid
cufes.plot.squid <- cufes %>% 
  filter(Density > 0, Species == "SquidEggs") %>% 
  arrange(desc(Density))

# Project CUFES data from other fish eggs (mostly P. mackerel)
cufes.plot.ofe <- cufes %>% 
  filter(Density > 0, Species == "OtherFishEggs") %>%
  filter(str_detect(Comments, c("Scomber japonicus","scomber japonicus",
                                "S. japonicus"))) %>% 
  arrange(desc(Density))
```  

```{r create-basemap,include=FALSE}
# Configure base map options -----------------
# Import landmarks
locations <- filter(read.csv(here("Data/Map/locations.csv")), name %in% label.list) %>%
  project_df(to = crs.proj)

# Get state data
states <- ne_states(country = 'United States of America', returnclass = 'sf')
ca     <- filter(states, name == "California")

# Get countries
countries <- ne_countries(scale = "large", returnclass = "sf") %>%
  filter(subregion %in% c("Northern America","Central America"))

# Read bathy contours shapefile 
bathy <- st_read(here("Data/GIS/bathy_contours.shp")) %>% 
  st_transform(crs.geog) %>% 
  rename(Depth = Contour)

# Set padding around data  
if (resize.map) {
  # Use nav data to resize map to survey progress
  map.bounds <- nav.paths.sf %>% 
    st_transform(crs = crs.proj) %>%
    st_bbox()  
} else {
  # Use nav data to resize map to survey progress
  map.bounds <- transects.sf %>%
    st_transform(crs = crs.proj) %>%
    st_bbox()  
}

# Determine map aspect ratio and set height and width
map.aspect <- (map.bounds$xmax - map.bounds$xmin)/(map.bounds$ymax - map.bounds$ymin)
map.height <- 10
map.width  <- map.height*map.aspect

# Create base map
base.map <- get_basemap(nav.paths.sf, states, countries, locations, bathy, map.bounds, crs = crs.proj) #+
# Add scalebar
# annotation_scale(style = "ticks", location = "br", height = unit(0.15, "cm"))

# Save the basemap
ggsave(base.map, file = here("Figs/fig_basemap.png"), 
       height = map.height, width = map.width)

save(base.map, file = here("Data/Map/basemap.Rdata"))
```

```{r create-static-maps}
if (save.figs) {
  # Create CUFES egg density maps
  source(here("Code/plot_cufes.R"))
}
```

```{r get-spatial-files,include=F}
# Import shapefiles ------------------------------------------------
# Read CA State Waters shapefile
ca_waters <- st_read(here("Data/GIS/ca_state_waters.shp")) %>% 
  st_transform(crs.geog)

or_waters <- st_read(here("Data/GIS/or_state_waters.shp")) %>% 
  st_transform(crs.geog)

# Read CA MPAs shapefile
ca_mpas <- st_read(here("Data/GIS/ca_mpas.shp")) %>% 
  st_transform(crs.geog) %>% 
  mutate(MPA = paste(NAME, Type))

or_mpas <- st_read(here("Data/GIS/or_mpas.shp")) %>% 
  st_transform(crs.geog) 

# Read CA MPAs shapefile
eez_usa <- st_read(here("Data/GIS/eez_us.shp")) %>% 
  st_transform(crs.geog)
eez_can <- st_read(here("Data/GIS/eez_canada.shp")) %>% 
  st_transform(crs.geog)
eez_mex <- st_read(here("Data/GIS/eez_mex.shp")) %>% 
  st_transform(crs.geog)

# Convert CUFES to sf; CRS - crs.geog
cufes.sf <- cufes %>% 
  filter(Density > 0, Species %in% cufes.plot.spp) %>%
  mutate(
    spp.label = case_when(
      Species == "SardineEggs" ~ "Sardine",
      Species == "AnchovyEggs" ~ "Anchovy",
      Species == "JackMackerelEggs"~ "Jack mackerel",
      TRUE ~ Species),
    label = paste(spp.label, " eggs: ", round(Density, 1), " /cubic m", sep = ""),
    popup = paste('<b>Species:', spp.label, '</b><br/>', round(Density, 1),"eggs m<sup>3</sup>")) %>% 
  st_as_sf(coords = c("long","lat"), crs = crs.geog) %>% 
  arrange(desc(Density))

cufes.squid.sf <- cufes %>% 
  filter(Density > 0, Species == "SquidEggs") %>%
  mutate(
    spp.label = case_when(
      Species == "SquidEggs" ~ "Squid",
      TRUE ~ Species),
    label = paste(spp.label, " eggs: ", round(Density, 1), " /cubic m", sep = ""),
    popup = paste('<b>Species:', spp.label, '</b><br/>', round(Density, 1),"eggs m<sup>3</sup>")) %>% 
  st_as_sf(coords = c("long","lat"), crs = crs.geog)

cufes.ofe.sf <- cufes %>% 
  filter(Density > 0, Species == "OtherFishEggs") %>%
  filter(str_detect(Comments, c("Scomber japonicus","scomber japonicus",
                                "S. japonicus"))) %>%
  mutate(
    spp.label = case_when(
      Species == "OtherFishEggs" ~ "Other fish",
      TRUE ~ Species),
    label = paste(spp.label, " eggs: ", round(Density, 1), " /cubic m", sep = ""),
    popup = paste('<b>Species:', spp.label, '</b><br/>', round(Density, 1),"eggs m<sup>3</sup><br/>", 
                  '</b>Comment:</b>', Comments)) %>% 
  st_as_sf(coords = c("long","lat"), crs = crs.geog)

# Convert negative CUFES samples to sf; CRS - crs.geog
cufes.neg.sf <- filter(cufes.raw, AllEggs == 0) %>% 
  mutate(bin.level = 1) %>% 
  st_as_sf(coords = c("long", "lat"), crs = crs.geog) %>% 
  select(SampleNumber, bin.level)
```

```{r create-leaflet-map, out.width="100%", out.height="8in"}
# Leaflet options
# https://rstudio.github.io/leaflet/

# Info on tile caching
# https://bhaskarvk.github.io/leaflet.extras/reference/TileCaching.html

# Set padding around data  
imap.bounds <- map_bounds(nav$lat, nav$long, 0.1) 

# Create color palette for MPAs
all.mpa.types <- as.factor(c(unique(as.character(ca_mpas$Type)), 
                             unique(as.character(or_mpas$Label))))

mpaPal  <- colorFactor(topo.colors(10), all.mpa.types)

# Create color pallette for CUFES
cufesPal <- colorFactor(cufes.colors, cufes.plot.spp)
# Create color palette for seep types
seepPal <- colorFactor(c("red","blue"), c("Seep","Uncertain"))
# Create color pallette for planned transects
txPal    <- colorFactor(wpt.colors, wpt.types)
trawlPal <- c('#00CD66', '#0000FF', '#A020F0',
              '#F5DEB3', '#00FFFF', '#FF0000')

# Plotting preferences -------------------------------------------------------
# Leaflet tile options; set both to T if caching
useCachedTile  <- F # Use cached tiles
useCrossOrigin <- F # USe cross origin

# Create leaflet map
i.map <- leaflet() %>% 
  # Enable tile caching
  enableTileCaching() %>% 
  # Add provider tiles; # http://leaflet-extras.github.io/leaflet-providers/preview/index.html
  addProviderTiles(providers$Esri.OceanBasemap, 
                   options = tileOptions(useCache = useCachedTile,
                                         crossOrigin = useCrossOrigin)) %>%
  # Add bathymetry contours
  addPolylines(data = bathy, color = "white", weight = 2, 
               label = ~paste(Depth, "m"), group = "Bathymetry Contours") %>% 
  # Add core planned transects
  addPolylines(data = filter(transects.sf, Type %in% c("Compulsory", "Adaptive")),
               color = ~txPal(Type), weight = 3, opacity = 0.5,
               label = ~htmlEscape(paste(Type, Transect)), 
               group = "Planned Transects (Core)") %>%
  addCircleMarkers(data = filter(wpts.sf, Type %in% c("Compulsory", "Adaptive")),
                   radius = 3, color = "#000414", stroke = F, opacity = 0.5,
                   fillOpacity = 0.5, fillColor =  ~txPal(Type), 
                   label = ~htmlEscape(paste(Type, Waypoint)),
                   group = "Planned Transects (Core)") %>%
  # Add nav data
  addPolylines(data = nav.paths.sf, color = "#000414", weight = 1, 
               label = ~leg, group = "Vessel Track") %>%
  # Add legends
  addLegend("bottomleft", colors = cufes.colors, 
            values = ~sort(unique(cufes.sf$Species)), 
            labels = cufes.spp.labels, 
            title = "CUFES Egg Density <br/> (eggs m<sup>-3</sup>)", 
            opacity = 1, group = "CUFES Egg Density") %>% 
  # Add scale bar
  addScaleBar(position = "bottomright") %>%
  # Add map coordinates
  addMouseCoordinates() %>% 
  # Add measurement tool
  addMeasure(primaryLengthUnit = "miles", secondaryLengthUnit = "km",
             primaryAreaUnit = "sqmiles", secondaryAreaUnit = "sqmeters",
             position = "topleft") %>% 
  # Add layer controls
  addLayersControl(
    overlayGroups = c("MPAs", "State Waters", "Exclusive Economic Zones", 
                      "Bathymetry Contours",
                      "Planned Transects (Core)", "Vessel Track", 
                      "CUFES Egg Density-Sardine", "CUFES Egg Density-Anchovy",
                      "CUFES Egg Density-Jack Mackerel", "CUFES Egg Density-Other",
                      "CUFES Egg Density-Squid", "CUFES (Negative)"),
    options = layersControlOptions(collapsed = F)) %>%  
  fitBounds(imap.bounds$range.lon[1], imap.bounds$range.lat[1],
            imap.bounds$range.lon[2], imap.bounds$range.lat[2])

# Add CUFES data
if (nrow(cufes.neg.sf) > 0)
  i.map <- i.map %>% 
  addCircleMarkers(data = cufes.neg.sf, radius = ~bin.level*2, color = "#000414", stroke = FALSE, weight = 1,
                   fillOpacity = 0.50, fillColor =  "#000414", label = ~htmlEscape(SampleNumber),
                   group = "CUFES (Negative)")
if (nrow(filter(cufes.sf, Species == "AnchovyEggs")) > 0)
  i.map <- i.map %>% 
  addCircleMarkers(data = filter(cufes.sf, Species == "AnchovyEggs"),
                   radius = ~bin.level*2, color = "#000414", stroke = TRUE, weight = 1,
                   fillOpacity = 0.75, fillColor =  ~cufesPal(Species), label = ~label,
                   popup = ~popup, group = "CUFES Egg Density-Anchovy")

if (nrow(filter(cufes.sf, Species == "JackMackerelEggs")) > 0)
  i.map <- i.map %>% 
  addCircleMarkers(data = filter(cufes.sf, Species == "JackMackerelEggs"),
                   radius = ~bin.level*2, color = "#000414", stroke = TRUE, weight = 1,
                   fillOpacity = 0.75, fillColor =  ~cufesPal(Species), label = ~label,
                   popup = ~popup, group = "CUFES Egg Density-Jack Mackerel")
if (nrow(filter(cufes.sf, Species == "SardineEggs")) > 0)
  i.map <- i.map %>% 
  addCircleMarkers(data = filter(cufes.sf, Species == "SardineEggs"),
                   radius = ~bin.level*2, color = "#000414", stroke = TRUE, weight = 1,
                   fillOpacity = 0.75, fillColor =  ~cufesPal(Species), label = ~label,
                   popup = ~popup, group = "CUFES Egg Density-Sardine")
if (nrow(cufes.squid.sf) > 0)
  i.map <- i.map %>% 
  addCircleMarkers(data = cufes.squid.sf,
                   radius = ~bin.level*2, color = "#000414", stroke = TRUE, weight = 1,
                   fillOpacity = 0.75, fillColor =  "#FFFFFF", label = ~label,
                   popup = ~popup, group = "CUFES Egg Density-Squid")
if (nrow(cufes.ofe.sf) > 0)
  i.map <- i.map %>% 
  addCircleMarkers(data = cufes.ofe.sf,
                   radius = ~bin.level*2, color = "#000414", stroke = TRUE, weight = 1,
                   fillOpacity = 0.75, fillColor =  pac.mack.color, label = ~label,
                   popup = ~popup, group = "CUFES Egg Density-Other") 

# Configure layer display
i.map <- i.map %>% 
    hideGroup(c("CUFES Egg Density-Squid", "Vessel Positions", "Planned Transects (Ancillary)"))
```

### Continuous Underway Fish Egg Sampler (CUFES) egg density for the `r survey.name` 

#### SWFSC Advanced Survey Technologies Group  

_**Last updated:**_ `r format(Sys.time(), "%F %T", tz = "America/Los_Angeles", usetz = TRUE)`

An interactive map of the CUFES egg density (eggs m^-3^) for anchovy, sardine, and jack mackerel. Other fish eggs (cyan points) are plotted that have Pacific mackerel eggs. Hover-over or click on some map objects for more info.  

```{r plot-leaflet-map, out.height = "12in", out.width="100%"}
# Display map
i.map
```

For questions about this page, please contact Kevin Stierhoff ([kevin.stierhoff@noaa.gov](mailto:kevin.stierhoff@noaa.gov)).
