---
output: 
  bookdown::html_document2:
    toc: no
  bookdown::pdf_document2:
    number_sections: no
    toc: no
    includes: 
      in_header: yaml/header_final.tex
  bookdown::word_document2:
    reference_docx: template/report_template_DRAFT_Rmarkdown.docx
csl: csl/ices-journal-of-marine-science.csl
bibliography: bib/ast_bib.bib
---

```{r load-libraries,echo=F,error=F,message=F,warning=F}
# Install and load pacman (library management package)
if (!require("pacman")) install.packages("pacman")

# Install and load required packages from CRAN ---------------------------------
pacman::p_load(tidyverse,grid,gridExtra,pander,flextable,lubridate, knitr,here,
               png,devtools,kableExtra,forcats,jpeg,bookdown,magick,
               odbc,cowplot,mapview,fs,sf)

# Install and load required packages from Github -------------------------------
# surveyR
pacman::p_load_gh("kstierhoff/surveyR")
pacman::p_load_gh("kstierhoff/atm")

# determines method of table generation (whether kable or xtable) for best formatting
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
if (is.null(doc.type)) {doc.type <- "html"}

# global knitr chunk options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      knitr.kable.NA = "-",
                      fig.align = "center",
                      dev = "png", dev.args = list(type = "cairo"))

# Set options for NA values in knitr::kable
options(knitr.kable.NA = '-')

# determine global knitr table format
if (doc.type == "latex") {
  knitr.format <- "latex"
} else {
  knitr.format <- "html" 
}

# global pander options
panderOptions('table.style','rmarkdown'); panderOptions('table.split.table', Inf); panderOptions('digits', 6);
panderOptions('round', 6); panderOptions('keep.trailing.zeros', T); panderOptions('missing', "")
```

```{r project-info, include=FALSE}
# Get project name from directory
prj.name <- last(unlist(str_split(here(),"/")))

# Get all settings files
settings.files <- dir(here("Doc/settings"))

# Source survey settings file
prj.settings <- settings.files[str_detect(settings.files, paste0("settings_", prj.name, ".R"))]
source(here("Doc/settings", prj.settings))
```

```{r user-controls}
# Processing settings
get.db     <- T
get.nav    <- T
do.spatial <- T
nav.source <- "ERDDAP" # Navigation data source: ERDDAP or SCS
save.figs  <- T
resize.map <- F # Resize map during survey; if T, uses anticipated bounds of survey area

# Sampling settings
sampling.cufes <- F
```

```{r get-trawl-data}
if (get.db) {
  # Source script to collect data from trawl database
  source(here("Code/collect_trawl_database.R"))
  
} else {
  # Load trawl data
  load(here("Data/Trawl/trawl_data_raw.Rdata"))
  
}
```

```{r format-trawl-data}
# Source script to format data from trawl database
source(here("Code/format_trawl_database.R"))
```

```{r process-trawl-data}
# if (trawl.source == "Access") {
#   if (year(haul.all$netInWaterTime[1]) >= 2021) {
#     haul.all <- haul.all %>% 
#       mutate(
#         startLatDecimal  =   startLatitudeDegrees + (startLatitudeMinutes/60),
#         startLongDecimal = -(startLongitudeDegrees + (startLongitudeMinutes/60)),
#         stopLatDecimal   =   stopLatitudeDegrees + (stopLatitudeMinutes/60),
#         stopLongDecimal  = -(stopLongitudeDegrees + (stopLongitudeMinutes/60))) %>% 
#       filter(cruise %in% cruise.name & ship %in% cruise.ship)
#     
#   } else {
#     haul.all <- haul.all %>% 
#       arrange(haul) %>% 
#       mutate(
#         startLatDecimal  =   startLatitudeDegrees + (startLatitudeMinutes/60),
#         startLongDecimal = -(startLongitudeDegrees + (startLongitudeMinutes/60)),
#         stopLatDecimal   =   stopLatitudeDegrees + (stopLatitudeMinutes/60),
#         stopLongDecimal  = -(stopLongitudeDegrees + (stopLongitudeMinutes/60)), 
#         equilibriumTime  =   ymd_hms(paste(as.character(trawlDate),
#                                            format(haul.all$EquilibriumTime,
#                                                   format = "%H:%M:%S"))),
#         haulBackTime     =   ymd_hms(paste(as.character(trawlDate),
#                                            format(haul.all$haulbackTime,
#                                                   format = "%H:%M:%S")))) %>%
#       mutate(haulBackTime = case_when(
#         haulBackTime < equilibriumTime ~ haulBackTime + days(1),
#         TRUE ~ haulBackTime)) %>%
#       rename(cruise = Cruise, ship = Ship, haul = Haul,
#              collection = Collection, notes = Notes) %>%
#       filter(cruise %in% cruise.name & ship %in% cruise.ship) 
#     
#     # Identify hauls where date of equilibriumTime or haulBackTime is incorrect
#     eq.fix <- which(c(0, diff(haul$equilibriumTime)) < 0)
#     hb.fix <- which(c(0, diff(haul$haulBackTime)) < 0)
#     
#     # Correct equilibriumTime or haulBackTime
#     haul.all$equilibriumTime[eq.fix] <- haul.all$equilibriumTime[eq.fix] + days(1)
#     haul.all$haulBackTime[eq.fix]    <- haul.all$haulBackTime[eq.fix] + days(1)
#   }
#   
# } else if (trawl.source == "SQL") {
#   # Filter haul data for current survey
#   haul.all <- haul.all %>% 
#     arrange(haul) %>% 
#     mutate(equilibriumTime = ymd_hms(equilibriumTime),
#            haulBackTime    = ymd_hms(haulBackTime)) %>% 
#     select(cruise,ship,haul,collection,startLatDecimal,startLongDecimal,stopLatDecimal,
#            stopLongDecimal,equilibriumTime,haulBackTime,trawlPerformance,notes) %>% 
#     filter(cruise %in% cruise.name & ship %in% cruise.ship) 
#   
# } else if (trawl.source == "Excel") {
#   # Format haul data
#   haul.all <- haul.all %>% 
#     mutate(
#       startLatDecimal  =   DecLatitude,
#       startLongDecimal =   DecLongitude,
#       stopLatDecimal   =   DecLatitude,
#       stopLongDecimal  =   DecLongitude,
#       equilibriumTime  =   mdy_hms(paste(as.character(trawlDate),
#                                          format(haul.all$EquilibriumTime, 
#                                                 format = "%H:%M:%S"))),
#       haulBackTime     =   equilibriumTime + minutes(`Duration(dec)`*60))
#   
#   # Filter haul data for current survey
#   haul.all <- haul.all %>% 
#     select(cruise = Cruise,ship = Ship,haul = Haul,collection = Collection,
#            startLatDecimal,startLongDecimal,stopLatDecimal,
#            stopLongDecimal,equilibriumTime,haulBackTime) %>% 
#     filter(cruise %in% cruise.name & ship %in% cruise.ship)
# }

# Filter haul data for current survey
haul <- haul.all %>% 
  select(cruise, ship, haul, collection, startLatDecimal, startLongDecimal, 
         stopLatDecimal, stopLongDecimal, equilibriumTime, haulBackTime, 
         trawlPerformance) %>% 
  filter(cruise %in% cruise.name & ship %in% cruise.ship) 

# Filter and format catch data
catch <- catch.all %>% 
  left_join(select(spp.codes, species, scientificName, commonName)) %>% 
  filter(cruise %in% cruise.name & ship %in% cruise.ship & netSampleType == 'codend') %>% 
  filter(!subSampleWtkg == 0) 

# Summarize species catch by weight and number
catch.summary <- catch %>% 
  # Subset columns
  select(haul, scientificName, commonName,
         totalWeight, totalNum) %>% 
  arrange(haul, desc(totalWeight)) %>% 
  # Add position data
  left_join(select(haul, haul, Latitude = startLatDecimal, 
                   Longitude = startLongDecimal))

# Rename columns
names(catch.summary) <- c("Haul","Scientific Name","Common Name",
                          "Total weight (kg)","Total number (n)",
                          "Latitude","Longitude")

# Write output files
write_csv(haul, here("Output/haul_table_ONMS.csv"))
write_csv(catch.summary, 
          here("Output/catch_table_ONMS.csv"))
```

```{r load-spatial-data, include = FALSE}
# Read EEZ shapefiles -----------------------------------------
eez_usa <- st_read(here("Data/GIS/eez_us.shp")) %>% 
  st_transform(crs.geog) %>% 
  select(geometry)
```

\blandscape  

# Trawl catch summary for the `r survey.name.long` (`r survey.name` )

## NOAA Fisheries-Southwest Fisheries Science Center

_**Last updated:**_ `r format(Sys.time(), "%F %T", tz = "America/Los_Angeles", usetz = TRUE)`

Catch for all trawl samples are summarized in the table below. Species are listed descending by weight. For hauls with large catches (i.e., > 5 baskets), the total number was estimated from the total weight and the average weight of specimens in the subsample.

```{r catch-table}
# Convert to datatable to allow for sorting/filtering?
kable(catch.summary, format = knitr.format, booktabs = TRUE, 
      escape = FALSE, longtable = TRUE,
      align           = c(rep("l", 3), rep("r", ncol(catch.summary) - 3)),
      digits          = c(0,0,0,3,0,4,4),
      format.args     = list(big.mark = ",")) %>% 
  kable_styling(latex_options = c("repeat_header","HOLD_position",
                                  "scale_down"),
                position = "center",
                font_size = 8) %>%
  column_spec(2, italic = T) 
```

For questions about the contents of this report, please contact Kevin Stierhoff ([kevin.stierhoff@noaa.gov](mailto:kevin.stierhoff@noaa.gov)).

\elandscape
