---
title: "PSIT Protected Species Catch and Specimen Reporting"
author: "Kevin Stierhoff"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    number_sections: yes
css: css/ast.css
---

```{r set-up, error=FALSE, message=FALSE, warning=FALSE, echo=F}
# Install and load pacman (library management package)
if (!require("pacman")) install.packages("pacman")

# Install and load required packages from CRAN ---------------------------------
pacman::p_load(tidyverse,swfscMisc,lubridate,sp,mapview,RODBC,
               knitr,geosphere,ggrepel,cowplot,sf,leaflet, htmltools,
               odbc,kableExtra,rnaturalearth,shadowtext,here,fs, RSQLite,
               ggspatial,janitor,DT)

# Install and load required packages from Github -------------------------------
# surveyR
pacman::p_load_gh("kstierhoff/surveyR")
pacman::p_load_gh("kstierhoff/atm")


# Define method of table generation (whether kable or xtable) for best formatting
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
if (is.null(doc.type)) {doc.type <- "html"}

# Set global knitr chunk options
if (.Platform$OS.type == "unix") {
  # Do not specify Cairo device for MacOS
  knitr::opts_chunk$set(echo = F, warning = F, message = F,
                        fig.align = 'center', out.width = '100%', dev = "png", dpi = 150)
} else {
  knitr::opts_chunk$set(echo = F, warning = F, message = F,
                        fig.align = 'center', out.width = '100%', dev = "png", dpi = 150,
                        dev.args = list(type = "cairo"))
}

# determine global knitr table format
if (doc.type == "latex") {
  knitr.format <- "latex"
} else {
  knitr.format <- "html" 
}
```

```{r project-info,include=FALSE}
# Get project name from directory
prj.name <- last(unlist(str_split(here(),"/")))

# Get all settings files
settings.files <- dir(here("Doc/settings"))

# Source survey settings file
prj.settings <- settings.files[str_detect(settings.files, paste0("settings_", prj.name, ".R"))]
source(here("Doc/settings", prj.settings))
```

```{r user-controls}
# Processing settings
get.db     <- T
get.nav    <- T
do.spatial <- T
nav.source <- "ERDDAP" # Navigation data source: ERDDAP or SCS
save.figs  <- T
resize.map <- F # Resize map during survey; if T, uses anticipated bounds of survey area

# Sampling settings
sampling.cufes <- F
```

```{r get-trawl-data}
if (get.db) {
  # Source script to collect data from trawl database
  source(here("Code/collect_trawl_database.R"))
  
} else {
  # Load trawl data
  load(here("Data/Trawl/trawl_data_raw.Rdata"))
  
}
```

```{r format-trawl-data}
# Source script to format data from trawl database
source(here("Code/format_trawl_database.R"))
```

```{r process-trawl-data}
# Clean and format haul data ---------------------------
haul.all <- haul.all %>% 
  # Remove bad trawls
  filter(!trawlPerformance %in% trawl.performance) %>%
  # Remove trawls from other surveys
  filter(cruise %in% cruise.name & ship %in% cruise.ship) %>% 
  mutate(duration = difftime(haulBackTime, equilibriumTime, units = "mins"), # Calculate duration
         cluster  = cumsum(c(0, diff(equilibriumTime)) > 12) + 1) # Assign cluster

# Filter catch and specimen data -------------------------------------
catch.all   <- filter(catch.all, cruise %in% haul.all$cruise)
lengths.all <- filter(lengths.all, cruise %in% haul.all$cruise)
```

```{r id-protected-spp}
# Trout & salmon: Pacific salmon unid., pink, chum, coho, sockeye, Chinook, steelhead
salmon   <- c(161931, 161974, 161975, 161976, 161977, 161979, 161980, 161989) 
eulachon <-   162051

# Filter non-protected species
protected.spp <- filter(spp.codes, species %in% c(salmon, eulachon))
```

```{r extract-catch}
# Extract catch containing protected species
catch.psit <- catch.all %>% 
  left_join(spp.codes) %>% 
  left_join(select(haul.all, haul, orderOcc, netInWaterTime, lat = startLatDecimal, long = startLongDecimal,
                   surfaceTempC, salinityPPM)) %>%
  filter(species %in% protected.spp$species) %>% 
  select(cruise,ship,haul,collection,species,commonName,scientificName,netInWaterTime,lat,long,
         remainingSubSampleWtkg,subSampleWtkg,subSampleCount,totalNum,totalWeight,
         isWtEstimated,hasLF,notes,netSampleType)

# Output to CSV
write_csv(catch.psit, 
          file = here("Output", paste0(survey.name, "_ProtectedSpeciesCatch_to_report_Compliance.csv")),
          na = "")
```

```{r extract-specimens}
# Extract specimens from protected species
lengths.psit <- lengths.all %>% 
  left_join(spp.codes) %>% 
  left_join(select(haul.all, haul, orderOcc, netInWaterTime, equilibriumTime, 
                   lat = startLatDecimal, long = startLongDecimal,
                   surfaceTempC, salinityPPM)) %>% 
  filter(species %in% protected.spp$species) %>% 
  select(cruise,ship,haul,collection,species,scientificName,commonName,specimenNumber,
         orderOcc,netInWaterTime,equilibriumTime,lat,long,surfaceTempC,salinityPPM,individual_ID,
         forkLength_mm,weightg,notes,wasFrozen,netSampleType,isAlive,
         otolithNumber,DNAvialNumber,adiposeCondition,hasDNAfinClip,hasTag)

# Output to CSV
write_csv(lengths.psit, 
          file = here("Output", paste0(survey.name, "_SalmonSpecimens_to_report_Compliance.csv")),
          na = "")
```

```{r seine-catch}
# Load seine data
if (file.exists(here("Output/purse_seine_sets.Rdata")))
  load(here("Output/purse_seine_sets.Rdata"))
if (file.exists(here("Output/purse_seine_catch.Rdata")))
  load(here("Output/purse_seine_catch.Rdata"))
if (file.exists(here("Output/purse_seine_lengths.Rdata")))
  load(here("Output/purse_seine_lengths.Rdata"))
```


```{r extract-catch-seine}
# Extract catch containing protected species
catch.seine.psit <- set.catch %>% 
  left_join(select(spp.codes, scientificName, commonName)) %>% 
  left_join(select(sets, key.set, vessel.name, datetime, lat, long)) %>%
  filter(scientificName %in% protected.spp$scientificName)

if (nrow(catch.seine.psit) > 0) {
  # Output to CSV
  write_csv(catch.seine.psit, 
            file = here("Output", paste0(survey.name, "_ProtectedSpeciesCatch_to_report_Compliance-Seine.csv")),
            na = "")  
}
```

```{r extract-specimens-seine}
# Extract specimens from protected species
lengths.seine.psit <- set.lengths %>% 
  left_join(select(spp.codes, scientificName, commonName)) %>% 
  left_join(select(sets, key.set, vessel.name, datetime, lat, long)) %>%
  filter(scientificName %in% protected.spp$scientificName)

if (nrow(lengths.seine.psit) > 0) {
  # Output to CSV
  write_csv(lengths.seine.psit, 
            file = here("Output", paste0(survey.name, "_SalmonSpecimens_to_report_Compliance-Seine.csv")),
            na = "")  
}
```

# Catch summary

A summary of catches from trawls containing protected species.

# Protected species catch 
## Catch summary
### Trawl

A summary of catches from trawls containing protected species.

```{r catch-table}
catch.psit %>% 
  select(cruise,ship,haul, netInWaterTime,commonName,scientificName,totalNum,totalWeight) %>% 
  datatable(rownames = FALSE)
```

### Seine

A summary of catches from seines containing protected species.

```{r catch-table-seine}
catch.seine.psit %>% 
  select(vessel.name,key.set,datetime,commonName,scientificName,totalNum,totalWeight) %>% 
  datatable(rownames = FALSE) 
```

# Protected species specimens
## Specimen info
### Trawl

Specimen info for protected species.

```{r specimen-table}
lengths.psit %>% 
  select(cruise,ship,haul,netInWaterTime,commonName,scientificName,specimenNumber,
         forkLength_mm,weightg) %>% 
  datatable(rownames = FALSE)
```

### Seine

Specimen info for protected species.

```{r specimen-table-seine}
lengths.seine.psit %>% 
  select(vessel.name, key.set, datetime,commonName,scientificName,forkLength_mm) %>% 
  datatable(rownames = FALSE) 
```

## Specimen summary
### Trawl

Trawl specimen summary for protected species.

```{r specimen-summary}
# Summarize specimens
lengths.psit.summary <- lengths.psit %>% 
  # Select specimens where weights, otoliths, and/or DNA were taken
  filter(!is.na(otolithNumber) | !is.na(DNAvialNumber) | 
           !is.na(weightg)) %>% 
  select(haul, commonName, scientificName, weightg, 
         otolithNumber, DNAvialNumber, hasDNAfinClip, adiposeCondition) %>% 
  group_by(haul, commonName, scientificName) %>% 
  # !is.na(var) converts to logical then sum gives the total counts
  summarise(measured = sum(!is.na(weightg)), 
            otoliths = sum(!is.na(otolithNumber)),
            DNA      = sum(!is.na(DNAvialNumber)),
            adipose_intact  = sum(adiposeCondition == "intact", na.rm = TRUE),
            adipose_clipped = sum(adiposeCondition == "clipped", na.rm = TRUE)) %>% 
  arrange(scientificName, haul)

# Output to CSV
write_csv(lengths.psit.summary, 
          file = here("Output", paste0(survey.name, "_ProtectedSpeciesSpecimenSummary_to_report_Compliance.csv")),
          na = "")

lengths.psit.summary %>% 
  adorn_totals() %>% 
  datatable(rownames = FALSE)
```

