---
output: 
  bookdown::html_document2:
    toc: no
  bookdown::pdf_document2:
    number_sections: no
    toc: no
    includes: 
      in_header: yaml/header_final.tex
  bookdown::word_document2:
    reference_docx: template/report_template_DRAFT_Rmarkdown.docx
csl: csl/ices-journal-of-marine-science.csl
bibliography: bib/ast_bib.bib
---

```{r load-libraries,echo=F,error=F,message=F,warning=F}
# Install and load pacman (library management package)
if (!require("pacman")) install.packages("pacman")

# Install and load required packages from CRAN ---------------------------------
pacman::p_load(tidyverse,grid,gridExtra,pander,flextable,lubridate, knitr,here,
               png,devtools,kableExtra,forcats,jpeg,bookdown,bookdownplus,magick,
               odbc,cowplot,mapview,fs,sf)

# Install and load required packages from Github -------------------------------
# surveyR
pacman::p_load_gh("kstierhoff/surveyR")
pacman::p_load_gh("kstierhoff/atm")

# determines method of table generation (whether kable or xtable) for best formatting
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
if (is.null(doc.type)) {doc.type <- "html"}

# global knitr chunk options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      knitr.kable.NA = "-",
                      fig.align = "center",
                      dev = "png", dev.args = list(type = "cairo"))

# Set options for NA values in knitr::kable
options(knitr.kable.NA = '-')

# determine global knitr table format
if (doc.type == "latex") {
  knitr.format <- "latex"
} else {
  knitr.format <- "html" 
}

# global pander options
panderOptions('table.style','rmarkdown'); panderOptions('table.split.table', Inf); panderOptions('digits', 6);
panderOptions('round', 6); panderOptions('keep.trailing.zeros', T); panderOptions('missing', "")
```

```{r project-info, include=FALSE}
# Get project name from directory
prj.name <- last(unlist(str_split(here(),"/")))

# Get all settings files
settings.files <- dir(here("Doc/settings"))

# Source survey settings file
prj.settings <- settings.files[str_detect(settings.files, paste0("settings_", prj.name, ".R"))]
source(here("Doc/settings", prj.settings))
```

```{r load-catch-data}
# Load haul and catch data
load(here("Data/Trawl/trawl_data.Rdata"))
```

```{r load-spatial-data, include = FALSE}
# Read EEZ shapefiles -----------------------------------------
eez_usa <- st_read(here("Data/GIS/eez_us.shp")) %>% 
  st_transform(crs.geog) %>% 
  select(geometry)
```

```{r process-hauls}
# Create startLatitudeDecimal and startLongitudeDecimal for Access data
if (trawl.source == "Access") {
  # Reformat haul data to match SQL
  haul.all <- haul.all %>% 
    mutate(
      startLatDecimal  =   startLatitudeDegrees + (startLatitudeMinutes/60),
      startLongDecimal = -(startLongitudeDegrees + (startLongitudeMinutes/60)),
      stopLatDecimal   =   stopLatitudeDegrees + (stopLatitudeMinutes/60),
      stopLongDecimal  = -(stopLongitudeDegrees + (stopLongitudeMinutes/60)), 
      haulBackTime     = haulbackTime,
      equilibriumTime  = EquilibriumTime) %>% 
    mutate(haulbackTime = case_when(
      haulBackTime < equilibriumTime ~ haulBackTime + days(1),
      TRUE ~ haulBackTime)) %>%
    rename(cruise = Cruise, ship = Ship, haul = Haul, 
           collection = Collection, notes = Notes)
  
  
} else if (trawl.source == "SQL") {
  haul.all <- haul.all %>% 
    mutate(
      equilibriumTime = ymd_hms(equilibriumTime),
      haulBackTime    = ymd_hms(haulBackTime))
  
  # Compute totalWeight and totalNum, which only exist in the Access database
  catch.all <- catch.all %>% 
    mutate(
      totalWeight = subSampleWtkg + remainingSubSampleWtkg,
      totalNum    = (subSampleCount/subSampleWtkg)*totalWeight)
  
}

# Filter haul data for current survey
haul <- haul.all %>% 
  select(cruise, ship, haul, collection, startLatDecimal, startLongDecimal, 
         stopLatDecimal, stopLongDecimal, equilibriumTime, haulBackTime, 
         trawlPerformance) %>% 
  filter(cruise %in% cruise.name & ship %in% cruise.ship) 

write_csv(haul, 
          here("Output/haul_table_ONMS.csv"))
```

```{r process-catch}
# Filter and format catch data
catch <- catch.all %>% 
  left_join(select(spp.codes, species, scientificName, commonName)) %>% 
  filter(cruise %in% cruise.name & ship %in% cruise.ship & netSampleType == 'codend') %>% 
  filter(!subSampleWtkg == 0) 

# Summarize species catch by weight and number
catch.summary <- catch %>% 
  mutate(totalWeight = subSampleWtkg + remainingSubSampleWtkg,
         totalNum = totalWeight/(subSampleWtkg/subSampleCount)) %>%
  group_by(haul, scientificName, commonName) %>% 
  summarise(totalWeight = sum(totalWeight),
            totalNum    = sum(totalNum)) %>% 
  arrange(haul, desc(totalWeight)) %>% 
  # Add position data
  left_join(select(haul, haul, Latitude = startLatDecimal, 
                   Longitude = startLongDecimal))

# Rename columns
names(catch.summary) <- c("Haul","Scientific Name","Common Name",
                          "Total weight (kg)","Total number (n)",
                          "Latitude","Longitude")

write_csv(catch.summary, 
          here("Output/catch_table_ONMS.csv"))
```

\blandscape  

# Trawl catch summary for the `r survey.name.long` (`r survey.name` )

## NOAA Fisheries-Southwest Fisheries Science Center

_**Last updated:**_ `r format(Sys.time(), "%F %T", tz = "America/Los_Angeles", usetz = TRUE)`

Catch for all trawl samples are summarized in the table below. Species are listed descending by weight. For hauls with large catches (i.e., > 5 baskets), the total number was estimated from the total weight and the average weight of specimens in the subsample.

```{r catch-table}
kable(catch.summary, format = knitr.format, booktabs = TRUE, 
      escape = FALSE, longtable = TRUE,
      align           = c(rep("l", 3), rep("r", ncol(catch.summary) - 3)),
      digits          = c(0,0,0,3,0,4,4),
      format.args     = list(big.mark = ",")) %>% 
  kable_styling(latex_options = c("repeat_header","HOLD_position",
                                  "scale_down"),
                position = "center",
                font_size = 8) %>%
  column_spec(2, italic = T) 
```

For questions about the contents of this report, please contact Kevin Stierhoff ([kevin.stierhoff@noaa.gov](mailto:kevin.stierhoff@noaa.gov)).

\elandscape
