---
output: 
  bookdown::pdf_document2:
    number_sections: no
    toc: no
    includes: 
      in_header: yaml/header_final.tex
---

```{r load-libraries,echo=F,error=F,message=F,warning=F}
# Install and load pacman (library management package)
if (!require("pacman")) install.packages("pacman")

# Install and load required packages from CRAN ---------------------------------
pacman::p_load(tidyverse,grid,gridExtra,pander,flextable,lubridate, knitr,here,
               png,devtools,kableExtra,forcats,jpeg,bookdown,magick,
               odbc,cowplot,mapview,fs,sf)

# Install and load required packages from Github -------------------------------
# surveyR
pacman::p_load_gh("kstierhoff/surveyR")
pacman::p_load_gh("kstierhoff/atm")

# determines method of table generation (whether kable or xtable) for best formatting
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
if (is.null(doc.type)) {doc.type <- "html"}

# global knitr chunk options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      knitr.kable.NA = "-",
                      fig.align = "center",
                      dev = "png", dev.args = list(type = "cairo"))

# Set options for NA values in knitr::kable
options(knitr.kable.NA = '-')

# determine global knitr table format
if (doc.type == "latex") {
  knitr.format <- "latex"
} else {
  knitr.format <- "html" 
}

# global pander options
panderOptions('table.style','rmarkdown'); panderOptions('table.split.table', Inf); panderOptions('digits', 6);
panderOptions('round', 6); panderOptions('keep.trailing.zeros', T); panderOptions('missing', "")
```

```{r project-info, include=FALSE}
# Get project name from directory
prj.name <- last(unlist(str_split(here(),"/")))

# Get all settings files
settings.files <- dir(here("Doc/settings"))

# Source survey settings file
prj.settings <- settings.files[str_detect(settings.files, paste0("settings_", prj.name, ".R"))]
source(here("Doc/settings", prj.settings))
```

```{r user-controls}
# Processing settings
get.db     <- T
get.nav    <- T
do.spatial <- T
nav.source <- "ERDDAP" # Navigation data source: ERDDAP or SCS
save.figs  <- T
resize.map <- F # Resize map during survey; if T, uses anticipated bounds of survey area

# Sampling settings
sampling.cufes <- F
```

```{r get-trawl-data}
if (get.db) {
  # Source script to collect data from trawl database
  source(here("Code/collect_trawl_database.R"))
  
} else {
  # Load trawl data
  load(here("Data/Trawl/trawl_data_raw.Rdata"))
  
}
```

```{r format-trawl-data}
# Source script to format data from trawl database
source(here("Code/format_trawl_database.R"))
```

```{r process-trawl-data}
haul.all <- haul.all %>% 
  # Remove bad trawls
  filter(!trawlPerformance %in% trawl.performance) %>%
  # Remove trawls from other surveys
  filter(cruise %in% cruise.name & ship %in% cruise.ship) %>% 
  mutate(duration = difftime(haulBackTime, equilibriumTime, units = "mins"), # Calculate duration
         cluster  = cumsum(c(0, diff(equilibriumTime)) > 12) + 1) # Assign cluster

# Find midpoint of each haul as the mean lat/lon
haul.mid <- haul.all %>% 
  group_by(cluster, haul) %>% 
  summarise(
    lat  = mean(c(startLatDecimal, stopLatDecimal)),
    long = mean(c(startLongDecimal, stopLongDecimal))) 

# Find midpoint of each haul cluster as the average of haul midpoints
cluster.mid <- haul.mid %>% 
  group_by(cluster) %>% 
  summarise(
    lat  = mean(lat),
    long = mean(long))

# Create haul paths from starts and ends
haul.paths <- select(haul.all, haul, lat = startLatDecimal, long = startLongDecimal) %>% 
  bind_rows(select(haul.all, haul, lat = stopLatDecimal, long = stopLongDecimal)) %>% 
  arrange(haul) %>% 
  st_as_sf(coords = c("long","lat"), crs = crs.geog) %>% 
  group_by(haul) %>% 
  summarise(do_union = F) %>% 
  st_cast("LINESTRING")
```

```{r process-hauls,include=FALSE}
# Read EEZ shapefiles -----------------------------------------
eez_usa <- st_read(here("Data/GIS/eez_us.shp")) %>% 
  st_transform(crs.geog) %>% 
  select(geometry)

# Filter haul data for current survey
haul <- haul.all %>% 
  select(cruise, ship, haul, collection, startLatDecimal, startLongDecimal, 
         stopLatDecimal, stopLongDecimal, equilibriumTime, haulBackTime, 
         trawlPerformance, Notes) %>% 
  filter(cruise %in% cruise.name & ship %in% cruise.ship) %>% 
  st_as_sf(coords = c("startLongDecimal","startLatDecimal"), crs = crs.geog) %>% 
  st_intersection(eez_usa)

# Get hauls inside the US EEZ
us.hauls <- sort(unique(haul$haul))
```

```{r process-catch}
# Filter and format catch data
catch <- catch.all %>% 
  left_join(select(spp.codes, species, scientificName, commonName)) %>% 
  filter(cruise %in% cruise.name & ship %in% cruise.ship & netSampleType == 'codend') %>% 
  filter(haul %in% us.hauls) %>% 
  filter(!subSampleWtkg == 0) 

# Summarize species catch by weight and number
catch.summary <- catch %>%
  select(scientificName, commonName, totalWeight, totalNum) %>%
  # Summarize catch by weight and number
  group_by(scientificName, commonName) %>% 
  summarize(totalWeight = sum(totalWeight),
            totalNum    = sum(totalNum)) %>% 
  arrange(desc(totalWeight)) 

# Rename columns
names(catch.summary) <- c("Scientific Name","Common Name",
                          "Total weight (kg)","Total number (n)")

write_csv(catch.summary, 
          here("Output/catch_table_WCRO.csv"))
```

\blandscape  

# Trawl catch summary for the `r survey.name.long` (`r survey.name` )

## NOAA Fisheries-Southwest Fisheries Science Center

_**Last updated:**_ `r format(Sys.time(), "%F %T", tz = "America/Los_Angeles", usetz = T)`

Catch for all trawl samples collected within the U.S. Exclusive Economic Zone (EEZ) are summarized in the table below. Species are listed descending by weight. For hauls with large catches (i.e., > 5 baskets), the total number was estimated from the total weight and the average weight of specimens in the subsample.  

```{r catch-table}
kable(catch.summary, format = knitr.format, booktabs = TRUE, 
      escape = FALSE, longtable = TRUE,
      align           = c(rep("l", 2), rep("r", ncol(catch.summary) - 2)),
      digits          = c(0,0,3,0),
      format.args     = list(big.mark = ",")) %>% 
  kable_styling(latex_options = c("repeat_header","HOLD_position",
                                  "scale_down"),
                position = "center",
                font_size = 8) %>%
  column_spec(1, italic = T) 
```

For questions about the contents of this report, please contact Kevin Stierhoff ([kevin.stierhoff@noaa.gov](mailto:kevin.stierhoff@noaa.gov)).

\elandscape
